---
title: "Assignment 3"
author: "XinYu Zhang"
date: "2023-11-01"
output:
  html_document: default
  pdf_document: default
---
##Question 1

Use sum() to determine the sum of numbers from 2000 to 20000. Provide your code and the actual sum in your answer.
```{r}
result<-sum(2000:20000)
result
#the sum from every number from 2000 to 20000
a<-5
b<-(2:20)
a
b
#numerical number a = 5
#numerical sequence from 2 to 20
```

##Question 2 In one or two sentences, describe what the above code snippet did.
```{r}
d<-"I just want to be deleted"
d
ls()
#list the object "d"
rm()
#remove the object "d"
```

##Question 3 do you get different results? If so, why?
```{r}
result<-a+b
result#numerical number a is added to every listed numerical number in "b" #(2+5) (3+5) (4+5)
result<-sum(a+b)
result#sum all the numerical number in object "a" and "b" #This sums up all the elements of the resulting vector from a + b #(2+5)+(3+5)+(4+5)...+(20+5) = 304

```

##Question 4  What is the sum of the 5th through 10th element of object b? Provide your code and the sum.
```{r}
result<-sum(b[5:10]) #5th through 10th element of object b
result
```

##Question 5 What is the sum of the 3rd, 8th, and 10th element of b?

```{r}
result<-sum(b[c(3, 8, 10)])#c means combine c(values) numeric vector containing the values 3,8,10 to index "b" vector 
result
```

##Question 6 When extracting from a 2-dimensional object, which number specifies rows and which specifies columns? What does m[3,] do? How can you extract the 3rd, 4th and 5th columns of m together as one object?

```{r}
m <- matrix(data=1:25,ncol=5,byrow=T)
m
m[5,5]
#creating a 5*5 matrix,
#the byrow argument determines how data is filled into the matrix.
#the numbers are filled row-wise into the matrix because byrow was set to TRUE.
#the first number inidcate the row, second number indicate the column
#[m3,] means all elements in the 3rd row

result<-m[ ,c(3,4,5)]
#combine 3rd,4th,5th columns of m together.
result

```
##Question 7What does the cbind command do? How about rbind? Create a new object “n” where the first row is a new row of numbers (your choice) and the following rows are the rows from matrix m. Optional: do the same but reverse the order of the rows from matrix m.
```{r}
result<-cbind(m,101:105)
#You have a matrix m.
#You also have a vector 101:105 that contains the numbers 101, 102, 103, 104, and 105.
#Using the cbind() function, you are adding this vector as a new column to the right side of matrix m. The result is a new matrix.
#cbind means column bind; rbind means row bind
result

n<-(50:54)
result<-rbind(n,m)
#row combine add a row
result

```

